\chapter*{Acknowledgments}
Firstly, I would like to express my sincere gratitude to Anna Delin, my advisor for letting me be part of her research group at KTH Royal Institute of Technology. I would love to thank her for the continuous support of my Ph.D. study and related research, for her patience, motivation, and immense knowledge. Her guidance helped me a lot in all the time of research leading to fulfilling this thesis as well. I could not have imagined having a better advisor and mentor for my Ph.D. studies. She is always keen on delivering the best help through weekly meetings despite her limited time. I learned and still learning much from her.
I do appreciate the continuous help, and fruitful inputs form my current of old group members (in alphabetical order): both Amina Mirsakiyeva and Fan Pan (for the much fun we had!), Johan Hellsvik, Lars Bergqvist, Mikael Råsander, Michele Visciarelli (much appreciated his help regarding this thesis), Pavel Bessarab, Reza Mahani, Simone Borlenghi. Moreover, I thank my friend and collaborator Anderson Smith for the patience and making me part of the community; Andy has always been keen on involving me in new ideas, projects and research direction discussions. Additionally, I appreciate the big help from Max Lemme for his constructive comments on our joint research projects. I appreciate the nice work with Xuge Fan and Arne Quellmalz and wish to continue our excellent ongoing projects. I would like to extend my gratitude for input from old friends who are always keen on helping me; Loay for his impressive checks on DFT chapter and Shady for his meaningful comments throughout the text. I also appreciate the help and support from close friends Mina for his thoughtful help and Lamis for her endless support. I would also like to include all other Ray2een! members (Bada, Walid, Ma7ma7, Bakr, Hatem) for their continuous encouragement as well as Ramy being always here. 
I do want to extend to the SeRC and the SNIC at the PDC, KTH as well as NSC and Abisko supercomputers.
\endinput